\thetitle

### 2021-05-07 paper/paper.tex
updated experiments

\paragraph{Medium Variability.} The results for medium variability in the system are presented in
Table~\ref{tbl:unif}, where a uniform demand interarrival time is used. We use the tuples
\(70-\Unif\), \(80-\Unif\), and \(90-\Unif\) to indicate the experimental setup of using uniform
demand interarrival times with a aimed bottleneck utilisation of \(70\%\), \(80\%\), or \(90\%\)
respectively. The results state the accumulated costs, averaged over all replications, for the work
in process (WIPC), the finished goods inventory (FGIC), the backorder costs (BOC), as well as the
sum of the finished good inventory and backorder costs (\fgibocName{}) and the sum over all three cost
centers (SUM). For a better insight in the timing performance we also provide the average shopfloor
throughput time (SFTT), i.e.\@ the average time an order spends in the system after being released
and until reaching the finished goods inventory, the finished goods inventory time (FGIT), as well
as the service level (SL). The later is given in percentage and states the percentage of orders that
were produced on time. Finally, the actual measured costs per period (Cost.p.P) and the by the
algorithm learned average reward \(\avgrew\) are stated. The tested methods are the deep Q-Learning
algorithm with discount factor \(0.99\) (\qlt{0.99}), the \ARA{} algorithm with discount factors
\(0.99\) (\rlt{0.99}) and \(1.00\) (\rlt{1.00}), as well as the backward infinite loading
technique \BIL{} with fixed lead times between \(1\) and \(4\) as indicated by the number
($\BILOne$-$\BILFour$).

For the case of medium variability with a utilisation of \(70\%\) (\(70-\Unif\)) we can see that
\(\BILTwo\) performs best in the sense of accumulated costs. The reinforcement learning algorithm
follow, where \rlt{0.99} is significantly better then the other two variants. The other \BIL{}
variants accumulate much more costs. For the timing one can see that \rlt{1.00} performs very good
with a service level of \(93.2\%\). Furthermore, the learned average reward \(\avgrew\) and actual
average reward are very similar for both \ARA{} variants. However, with \(70\%\) of utilisation the
overhead of the reinforcement learning variants are too big to be able to compete with the simple
rule based release mechanism of \(\BILTwo{}\) as for changing workload the utilisation changes
rather linearly due to the low variability in the system.

In the case of \(80-\Unif\)

@@

@@

>>>>

\paragraph{Medium Demand Variability.} The results for medium variability in the system are
presented in Table~\ref{tbl:unif}, where a uniform demand interarrival time is used. We use the
tuples 70-\(\Unif\), 80-\(\Unif\), and 90-\(\Unif\) to indicate the experimental setup of using
uniform demand interarrival times with a aimed bottleneck utilisation of \(70\%\), \(80\%\), or
\(90\%\) respectively. The results state the accumulated costs, averaged over all replications, for
the work in process (WIPC), the finished goods inventory (FGIC), the backorder costs (BOC), as well
as the sum of the finished good inventory and backorder costs (\fgibocName{}) and the sum over all
three cost centers (SUM). To ease readability all costs are given in \(1000\)~Dollars. For a better
insight in the timing performance we also provide the average shopfloor throughput time (SFTT),
i.e.\@ the average time an order spends in the system after being released and until reaching the
finished goods inventory, the finished goods inventory time (FGIT), as well as the service level
(SL). The later is given in percentage and states the percentage of orders that were produced on
time. Finally, the actual measured costs per period (Cost.p.P) and the by the algorithm learned
average reward \(\avgrew\) are stated. The tested methods are the deep Q-Learning algorithm with
discount factor \(0.99\) (\qlt{0.99}), the \ARA{} algorithm with discount factors \(0.99\)
(\rlt{0.99}) and \(1.00\) (\rlt{1.00}), as well as the backward infinite loading technique \BIL{}
with fixed lead times between \(1\) and \(4\) as indicated by the number ($\BILOne$-$\BILFour$).

For the case of medium variability with a utilisation of \(70\%\) 70-(\(\Unif\)) we can see that
\(\BILTwo\) performs best in the sense of accumulated costs (\(220.53\)). The reinforcement learning
algorithm follow, where \rlt{0.99} is slightly but significantly better then the other two variants
(\(250.70\), \(254.97\), \(255.06\)). The other \BIL{} variants accumulate much more costs. For the
timing one can see that \rlt{1.00} performs very good with a service level of \(93.2\%\).
Furthermore, the learned average reward \(\avgrew\) and actual average reward are very similar for
both \ARA{} variants. However, with \(70\%\) of utilisation the overhead of the reinforcement
learning variants are too big to be able to compete with the simple rule based release mechanism of
\BILTwo{} as for changing workload the utilisation changes rather linearly due to the low
variability in the system.

In the case of 80-\(\Unif\) the deep Q-Learning variant \qlt{0.99} performs best in the cost related
measures (\(365.03\) for SUM), followed by \BILThree{} (\(369.97\)) and \rlt{1.00} (\(370.99\)),
which are not significantly different from each other. One can see the \BILTwo{} (\(377.27\))
performs slightly worse than \rlt{1.00} and is followed by \rlt{0.99} (\(382.39\)). Again \rlt{1.00}
achieves a very high service level of \(93.4\%\) with reasonable sum of cost, which is also
reflected in the low Backorder costs. Furthermore, the measured and learned average reward values
are quite close. Thus, the results already provide the insight that \ARA{} performs quite well in
terms of timing for the completion of orders. This pays off when confronted with higher
probabilistic systems.

For instance, with \(90\%\) utilisation and medium variable demand stream, i.e.\@ 90-(\(\Unif\)), we
can see that \rlt{0.99} performs best (\(576.48\)), followed by \qlt{0.99} (\(586.92\)) and
\BILThree{} (\(595.35\)), as well as \rlt{1.00} (\(602.54\)), where the later two are not
significantly different. In this case \rlt{0.99} also achieves the best service level of \(87.9\%\)
within this group of best performing algorithms. The WIPC costs, as well as the SFTT, show that the
reinforcement learning agents have a higher work-in-process, which is clear as they try to smooth
the workload of demand stream. When looking at the timing cost it becomes even more apparent that
the agents perform well in timing as \rlt{0.99} performs much better (\(471.13\)) than the other two
agents (\(488.01\), \(494.66\)) and all the \BIL{} techniques accumulated more \fgibocName{} costs
(\(507.10\) for the best performing \BIL{}, \BILThree{}).

@@

\paragraph{High Demand Variability.} For results of the experiments using exponential demand
interarrival times, presented in Table~\ref{tbl:exp} we can see a similar pattern as before. In this
case we use the tuples 70-\(\Exp\), 80-\(\Exp\), and 90-\(\Exp\) to indicate the corresponding
experimental setups.

For \(70\%\) utilization of the bottleneck, i.e. 80-\(\Exp\), \BILThree{} performs best with costs
of \(345.80\), followed by \rlt{0.99} with \(358.41\), and then by \qlt{0.99} and \BILTwo{}
(\(360.70\), \(364.18\)). In terms of timing performance, again \ARA{} outperforms the opponents
with \fgibocName{} costs of \(296.99\), and \BILThree{} with the second highest costs (\(297.17\)).
However, the service level of \BILThree{} is higher with \(93.7\%\) due to the lower shop floor
throughput time (SFTT, \(1.48\) for \BILThree{} versus \(1.73\) for \rlt{0.99}).

@@

\MS[t]{Job shop}
